\pdfoutput=1
\documentclass[11pt,a4paper]{article}
\usepackage{jheppub}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage{pgfplots}
\usepackage[makeroom]{cancel}
\pgfplotsset{compat=1.18}
\notoc

\title{Introduction to Supersymmetry}
\author{Edward Witten\note{Supported in part by NSF Grant PHY80-19754.}}
\affiliation{Joseph Henry Laboratories,\\
Princeton University,\\
Princeton, New Jersey 08544}

\begin{document}
\maketitle
\flushbottom

\section{Introduction}

Supersymmetry is a remarkable subject that has fascinated
particle physicists since it was originally introduced.\textsuperscript{1}
Although supersymmetry is no longer a new idea, we still do not know in what
form, if any, it plays a role in the proper description of nature.

The present status of supersymmetry might be compared very
roughly to the status of non-Abelian gauge theories twenty years ago.
It is a fascinating mathematical structure, and a reasonable extension
of current ideas, but plagued with phenomenological difficulties.

In these lectures, I will present an introduction to supersymmetry,
or at least to some aspects of this extensive subject. I
also will describe some recent results. Supersymmetry has the reputation
of a subject that is difficult to learn. I will try to at
least partially dispel this unjustified impression.

In these lectures we will discuss only global supersymmetry,
not supergravity.

A number of useful reviews of supersymmetry are available,
which approach the subject from several points of view.\textsuperscript{2}
Many aspects of supersymmetry that I will not be able to discuss are
treated in these review articles.

\section{Bose-Fermi Symmetry}

If one considers a theory of two decoupled Bose fields, $\phi_1$, and
$\phi_2$, so
\begin{equation}
\mathcal{L} = \int d^4x \, \frac{1}{2}\left((\partial_\mu \phi_1)^2 + (\partial_\mu \phi_2)^2\right)
\tag{1}
\end{equation}
it is possible to combine $\phi_1$ and $\phi_2$ into a conserved current
\[
J_\mu = \phi_1\, \partial_\mu \phi_2 - \phi_2\, \partial_\mu \phi_1
\]
even though they are not interacting.
Actually, since, for example, $\partial_\alpha \phi_1$ or
$\partial_\alpha \partial_\beta \phi_1$ satisfies the Klein-Gordon
equation just as $\phi_1$ does, one can form in the free field
theory additional conserved currents such as
\begin{align}
J_{\mu\alpha} &= \partial_\alpha \phi_1\, \partial_\mu \phi_2 - \phi_2\, \partial_\mu \partial_\alpha \phi_1 \notag\\
J_{\mu\alpha\beta} &= \partial_\alpha \partial_\beta \phi_1\, \partial_\mu \phi_2 - \phi_2\, \partial_\mu \partial_\alpha \partial_\beta \phi_1
\tag{2}
\end{align}
It is easy to check that these are conserved because
$\nabla^2 \phi_1 = \nabla^2 \phi_2 = 0$.

The reason that $J_\mu$ is far more important than $J_{\mu\alpha}$ or
$J_{\mu\alpha\beta}$ is that $J_\mu$ can still be conserved in interacting
theories. One can add to $\mathcal{L}$ a term like $V(\phi_1^2 + \phi_2^2)$
that is invariant under $\delta \phi_1 = \phi_2$, $\delta \phi_2 = -\phi_1$.
$J_\mu$ is still conserved.

However, when interactions are included, $J_{\mu\alpha}$ and $J_{\mu\alpha\beta}$
are no longer conserved. Moreover, it is not possible to redefine them (by
adding extra terms to allow for the interactions) so that they will still be
conserved. One may readily verify this in special cases. In general, it is a
consequence of the Coleman-Mandula theorem.\textsuperscript{3} Coleman and
Mandula showed (basically by S matrix theory alone) that in a theory with
non-zero scattering amplitudes in more than 1+1

\input{chunks/pp307-311.tex}

\end{document}
