% Original pages: 322--326
% Figures: none.
% Uncertainty log:
% - Original p. 322 begins mid-word ("...symmetry"); this chunk preserves the visible assigned-page text.
% - Original p. 323 appears to show a stray apostrophe in "mass' scale"; transcribed as visible below.
% - Minor scan specks on pp. 322--323 affect punctuation in a few places; obvious non-text marks were not promoted to content.

symmetry would get masses. Some scalars would get positive mass
squared; some would get negative mass squared. If the W boson gets
a mass from a Higgs doublet that gets an expectation value in this
way, we would get a hierarchy of some sort, with $(M_W/M_X)^2$ perhaps of
order $\alpha$ or $\alpha^2$. This clearly would fall far short of the experimentally
observed hierarchy.

However, a most remarkable theorem\textsuperscript{10} states that this does not
occur. It states that if at some point in field space the classical
potential vanishes, then the effective potential vanishes at that
point to all finite orders of perturbation theory. Our degeneracy
is not lifted in perturbation theory.

This fact is an example of the ``non-renormalization theorems''
of supersymmetry. Here are some other examples:

(1) There is no renormalization of $W$ in perturbation theory ---
neither finite nor infinite renormalization. (There is wave function
renormalization. There are quantum corrections to the effective
potential. There is no renormalization of $W$, if properly defined in
terms of the coefficients of certain operators in the effective
potential.)

(2) As long as supersymmetry is unbroken, any particle that is
massless at the tree level is massless to all finite orders of perturbation
theory --- even if it was massless at the tree level only
because of an arbitrary adjustment of parameters.

These theorems have been proved --- on the basis of details of
perturbation theory --- but they are not well understood.

Returning to our model with the three degenerate vacuum states,
if the relation $\langle \Omega| H |\Omega \rangle = 0$ were to break down in perturbation
theory, and if this breakdown were the origin of the ``light'' masses,
the resulting mass ratios would, as we have said, not be small enough
to solve Dirac's problem of the large numbers. However, if the mysterious
theorem concerning non-renormalization of $\langle \Omega| H |\Omega \rangle$ were to
break down non-perturbatively --- as it does in a quantum mechanics
model discussed in ref. (6) --- then we might obtain a solution to
the large number problem. We might get a formula of the form
\begin{equation}
\frac{M_W}{M_X} \sim \exp - \frac{1}{\alpha}
\tag{28}
\end{equation}
and this could solve the ``large number'' or ``gauge hierarchy'' problem.

% VERIFY: original scan appears to show "mass' scale" on p. 323.
We are thus imagining a theory with two mass scales. At the
large mass' scale, the scale of grand unification, a unified group
breaks down to $SU(3) \times SU(2) \times U(1)$, or some other phenomenologically
acceptable group, but supersymmetry remains unbroken. At a vastly
smaller mass scale, the non-renormalization theorems break down,
supersymmetry is spontaneously broken, and the Higgs boson gets an
expectation value, breaking $SU(2) \times U(1)$ down to $U(1)$.

What mechanism might be responsible for the tiny, non-perturbative
effects that make $\langle \Omega| H |\Omega \rangle$ non-zero and break supersymmetry?
With the present state of our knowledge, there are two obvious candidates.
The obvious candidates are strong gauge forces, and grand
unified instantons.

Let us discuss first the effects of strong gauge forces. Consider,
as an example, the $SU(5)$ theory that we discussed earlier.
Assume that the $SU(5)$ coupling is gauged; this can be done in a way
compatible with supersymmetry and with our previous remarks. In each
of the three vacuum states that exist in perturbation theory, there
is an unbroken non-Abelian interaction that will become strong at low
enough energies. For instance, in the vacuum at $\lambda_1 = 0$, this is the
full $SU(5)$ group. As we have learned in the last few years, strong
gauge forces cause a variety of non-perturbative effects, including
confinement, mass generation, and chiral symmetry breaking. Perhaps
in supersymmetric theories strong gauge forces also cause supersymmetry
breaking, presumably with the binding of a color singlet
Goldstone fermion.\textsuperscript{6,11}

Of course, in this $SU(5)$ theory, the vacuum of most phenomenological
interest is the one in which the unbroken gauge group is
$SU(3) \times SU(2) \times U(1)$. In this vacuum there are strong $SU(3)$ gauge
forces. But if they were responsible for supersymmetry breaking, we
would get bose-fermi mass differences of order $\Lambda_{\mathrm{QCD}}$ (since that is
the energy at which $SU(3)$ becomes strong), and this is clearly unsatisfactory.

In the same theory a more promising mechanism would be ``grand
unified instantons,'' that is, instantons of the $SU(5)$ group which
do not lie in the unbroken $SU(3) \times SU(2) \times U(1)$ subgroup. Such
instantons are not afflicted with infrared divergences. They have
a natural mass scale, the mass $M_X$ of grand unification, and a natural,
small coupling, the coupling $\alpha_G$ of grand unification. If such instantons
were responsible for supersymmetry breaking, we would get
bose-fermi mass splittings roughly of the order
\begin{equation}
m_B^2 - m_F^2 \sim M_X^2 \exp - \frac{2\pi}{\alpha_G}
\tag{29}
\end{equation}
which might be reasonable, for $\alpha_G$ of about $1/12$.

Actually, the instanton mechanism seems to work in $2+1$ dimensions,
but, apparently, not in $3+1$ dimensions.\textsuperscript{6} This point is in
need of further clarification.

Clearly, we must learn to analyze supersymmetry breaking in a
non-perturbative way. Tomorrow, I will describe some steps in that
direction. We will be able to derive some constraints on the possibility
of supersymmetry breaking by strong gauge forces.

\section[Tr(-1)^F]{Tr$(-1)^F$}

In our previous discussions we have seen that, in general, it
is difficult to determine from an approximate calculation whether
supersymmetry is spontaneously broken. Even if the supersymmetry
seems to be unbroken in some approximation, it is always possible
that a small, non-zero vacuum energy is induced by the corrections
to the approximation in question.

To show that supersymmetry is unbroken in a given theory one
must prove that the ground state energy is exactly zero. Since an
approximate calculation will not accomplish this, in general, we
must search for other methods. I will now describe an indirect
method which in some theories can be used to prove that the ground
state energy is exactly zero. Of course, a theory in which supersymmetry
is not broken is not a candidate for describing nature. The
purpose of proving that some theories do not break supersymmetry is
to cut down on the range of options that must be considered.

As a technical convenience, we will formulate our theories in a
finite volume, with periodic boundary conditions (such boundary conditions
respect supersymmetry). Our goal is to find criteria under
which we can prove that the ground state energy of a theory $E_0(V)$ is
zero in any finite volume $V$. Since the large $V$ limit of zero is zero,
this implies that the ground state energy is also zero in the infinite
volume limit, and therefore that supersymmetry is not broken in the
infinite volume theory which is of real interest.

Supersymmetry implies that every state of $E = 0$ also has $\vec P = 0$.
(Supersymmetry implies $E \geq 0$ in each frame; by Lorentz invariance
this requires $E \geq |\vec P|$; so a state of zero energy necessarily has
$\vec P = 0$.) So, in trying to determine whether the ground state energy
vanishes, we lose nothing by restricting ourselves to the sector of
Hilbert space consisting of states of $\vec P = 0$.

Let $Q$ be any one of the (hermitian) supersymmetry generators.
There are several $Q_\alpha$, of course, but we will only need one. In the
$\vec P = 0$ sector, the supersymmetry algebra is particularly simple. It
is simply
\begin{equation}
Q^2 = \frac{1}{2}\, H
\tag{30}
\end{equation}
(For nonzero $\vec P$, $\not\!P$ would appear on the right-hand side of (30).)

Since $Q^2 = \frac{1}{2}\, H$, $Q$ annihilates any states of zero energy. States
of non-zero energy are not annihilated by $Q$. Rather, they are paired
by the action of $Q$. Given any boson state $|b\rangle$ of non-zero energy $E$,
$Q$ acting on $|b\rangle$ gives a fermion state $|f\rangle$. $Q$ acting on $|f\rangle$ gives
back $|b\rangle$. To be precise
\begin{equation}
\begin{aligned}
Q\, |b\rangle &= \sqrt{\frac{E}{2}}\, |f\rangle \\
Q\, |f\rangle &= \sqrt{\frac{E}{2}}\, |b\rangle .
\end{aligned}
\tag{31}
\end{equation}
if phases are chosen properly. (Because $Q^2 = \frac{1}{2}\, H$, the factors of
$\sqrt{\frac{E}{2}}$ are consistent with $\langle b|b\rangle = \langle f|f\rangle = 1$, and the fact that $Q$ is
hermitian.)

I should explain that when I refer to a boson state $|b\rangle$, I do
not mean a one particle state (a concept that in a finite volume is
not really well defined) but any state of integral angular momentum.
Likewise, $|f\rangle$ is any state of half integral angular momentum. ``Here,
``angular momentum'' refers to the $90^\circ$ rotations such as $\exp - \frac{1}{2} i\pi J_z$
which are well defined in the finite volume theory. If we define
the operator
\begin{equation}
(-1)^F = \exp - 2\pi i J_z
\tag{32}
\end{equation}
which distinguishes bosons from germions, then a boson state $|b\rangle$ is
any state that obeys $(-1)^F |b\rangle = |b\rangle$, and a fermion state $|f\rangle$ is any
state that obeys $(-1)^F |f\rangle = -|f\rangle$. A boson state could be, for
