% Original pages: 347--351
% Figures: none.
% Uncertainty log: Original p. 347 begins with equation (53) and a mass symbol that is faint in the scan; Georgi's 75-plet field index structure is also faint on p. 348; original p. 351 ends mid-sentence.

% VERIFY: In equation (53), the mass parameter after the minus sign appears to be a script/calligraphic M in the scan.
\begin{equation}
\Delta W = \frac{g}{2}\, Z \left(C^i D_i - \mathcal{M}^2\right) + \lambda A^i_{\ j} C^j D_i
\tag{53}
\end{equation}

% VERIFY: The first mass symbol in the following sentence matches the faint scripted symbol in (53).
We assume that $\mathcal{M}$ is of order $M$. Minimization of the potential forces
$C$ and $D$ to obtain vacuum expectation values, spontaneously breaking
$SU(2) \times U(1)$ down to $U(1)$.

In this model, $SU(5)$ is broken to $SU(3) \times SU(2) \times U(1)$ at the
energy scale $X$, but supersymmetry is broken, and $SU(2) \times U(1)$ is
broken down to $U(1)$, at the far lower scale $M$. We thus obtain the
desired pattern of symmetry breaking. However, there are some severe
difficulties.

Perhaps the most severe difficulty is related to the fact that
the color triplet components of $C$ and $D$ are relatively ``light,''
with masses of order $M$. After introducing quarks and leptons in the
model, we must couple the $SU(2) \times U(1)$ doublet components of $C$ and $D$
to the quarks and leptons, in order to account for their bare masses.
However, $SU(5)$ then requires that we also couple the color triplet
components of $C$ and $D$ to the quarks and leptons. Unfortunately,
these color triplets then mediate a very rapid decay of the proton,
the lifetime being a small fraction of a second.

This particular problem can be avoided if we replace the coupling
$\lambda A^i_{\ j} C^j D_i$ in equation (53) with a term $\gamma Y^i_{\ j} C^j D_i$. In this case,
for reasons explained in reference (14), the color triplet components
of $C$ and $D$ automatically become superheavy without any special
adjustment of parameters. We can now couple $C$ and $D$ to quarks and
leptons, so as to account for the quark and lepton masses, without
inducing a rapid proton decay.

Unfortunately,\textsuperscript{14} the new coupling also modifies the pattern of
symmetry breaking. The vacuum expectation value of $Y$ is changed.
We now find that $SU(5)$ is strongly broken down to $SU(3) \times U(1) \times U(1)$
at the large mass scale $X$; $SU(3) \times U(1) \times U(1)$ is then broken to
$SU(3) \times U(1)$ at energies of order $M$. In this model the neutral
currents have roughly the strength that they actually have in nature,
but the charged currents are greatly suppressed.

It is difficult to simultaneously obtain the right pattern of
symmetry breaking and a suitably long proton lifetime. Recently,
% VERIFY: The field index structure in the scan is faint; it appears to be $Y^{ij}_{kl}$.
Georgi has described\textsuperscript{18} an attempt to do this, based on a model with
fields $Y^{ij}_{kl}$ in the 75 dimensional representation of $SU(5)$.

There is another crucial fact which must be borne in mind in
thinking about the phenomenology of these models. It turns out that
in the models as I have written them, the Goldstone fermion decouples
in the limit as $X$ becomes very large.\begingroup\renewcommand{\thefootnote}{\fnsymbol{footnote}}\footnotemark[1]\endgroup\ This means that although
supersymmetry is broken, the bosons and fermions are degenerate to
within terms of much less than $M$. Clearly, this is a very unacceptable
state of affairs if $M$ is interpreted as the mass scale of weak
interactions.

It is possible to avoid this decoupling of the Goldstone fermion,
and obtain models with bose-fermi splittings that really are of order
$M$, by adding additional fields. However, the resulting models seem
somewhat contrived.

It is equally interesting to explore the physical content of
our models such as (49) more carefully, bearing in mind the decoupling
of the Goldstone fermion. A more careful study of the model
based on equation (49) shows that, at the tree level, many particles
have masses much less than $M$. The $SU(3) \times SU(2) \times U(1)$ gauge mesons
and their fermionic partners are massless at the tree level. All
components of $Y$ except the component with a vacuum expectation value
have masses of order $M^2/X$. (As $X$ becomes large, $A$ becomes heavy and
decouples; as $A$ decouples, $Y$ becomes massless.) One would naively
expect that these light particles would receive masses of order $\alpha M$
or perhaps $\alpha^2 M$ from one or two loop diagrams. Because of the
decoupling of the Goldstone fermion and the non-renormalization theorems
of unbroken supersymmetry, this is not true. The particles
whose masses are of order $M^2/X$ or less at the tree level receive mass
corrections at most of order $\alpha M^2/X$ from the loop diagrams.

\begingroup
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{I wish to thank T. Banks for convincing me of this.}
\endgroup

These theories thus have three mass scales, $X$, $M$, and $M^2/X$, if
we do not attempt to tamper with the decoupling of the Goldstone
fermion that occurs for large $X$ in the simplest models. The fascinating
possibility exists that it is the smallest of these scales, the
scale $M^2/X$, which is the mass scale of particle physics as we know it.
One reason that this possibility is interesting is that at energies
of order $M^2/X$, supersymmetry appears to be explicitly (but softly)
broken. To write an effective Lagrangian describing this system in
which the supersymmetry is spontaneously broken, one must re-introduce
some of the degrees of freedom with masses of order $M$.

Of course, soft, explicit breaking of supersymmetry greatly
weakens the constraints associated with supersymmetry and thereby
alleviates the problems in finding a realistic model. The question
of finding a realistic model in which the mass scale of weak interactions
is the smallest scale, $M^2/X$, is therefore very much worthy
of attention. I will return to this matter elsewhere.\textsuperscript{19} One must,
of course, decide on an appropriate identification of $X$ and $M$.
Plausibly, in this approach, $X$ might be of order the Planck mass;
$M$ would then have to be about $10^{11}$ GeV.

Let us now conclude by discussing a few general questions.

In a theory in which the fundamental mass scale of nature is
relatively ``small'' and the mass of grand unification is a derived
quantity, we do not wish to assume that the Planck mass $M_{\rm Pl}$ is a
fundamental constant of nature. If it is, we are left with the large
and unexplained ratio $M_{\rm Pl}/M$. Rather, we should assume that the large
value of the Planck mass is spontaneously generated along with the
large value of the mass scale of grand unification.

This possibility is not as bizarre as it might sound. The
usual kinetic energy of the gravitational field is $M_0^2 R$, $M_0$ being
the bare Planck mass and $R$ the Ricci scalar. Another possible
coupling is the dimension four Brans-Dicke coupling $\lambda^2 |X|^2 R$, $X$ being the
scalar field that will eventually obtain a large vacuum expectation
value. (Such couplings actually arise almost inevitably when theories
of global supersymmetry are coupled to gravity.) We thus
imagine the gravitational action to be
\begin{equation}
\mathcal{L}_{\rm grav} = M_0^2 R + \lambda^2 |X|^2 R
\tag{54}
\end{equation}
where $\lambda$ is a constant of order one.

Clearly, the observed Planck mass would be $M_{\rm Pl}^2 = M_0^2 + \lambda^2 |X|^2$.
For large $X$, the Planck mass is simply $\lambda X$, unrelated to the original
constant $M_0$.

Let us now return to the question of how the effective potential
behaves when $X$ becomes very large. As we discussed earlier, while it
is possible that a stable minimum develops for large $X$, it is equally
possible that the potential decreases indefinitely with increasing $X$,
as in figure (16b).

This possibility corresponds to a world without a stable vacuum.
However, it is possible to expand about a ``cosmological solution'' in
which $X$ is regarded as a function of time. For large times, $X$ would
change very slowly, because the potential (being bounded below) is
nearly independent of $X$ for large $X$.

For instance, if $V(X) \sim v |X|^{-p}$ for some $p$, then, by solving the
cosmological equations (with the gravitational action taking the form
(54)), it is easy to show that for large $t$, $X \sim t^{2/(2+p)}$.

Since the masses and couplings of the elementary particles
depend on $X$, this corresponds to Dirac's idea that the ``constants''
of nature are slowly evolving functions of time. For instance,
Newton's constant $G = 1/M_{\rm Pl}^2$ scales with $X$ as $1/X^2$, because $M_{\rm Pl} \sim X$.
So $G \sim t^{-4/(2+p)}$, $t$ being the age of the universe. This may be compared
to the behavior $G \sim 1/t$ which Dirac advocated in order to account
for the value of $G$ in today's universe.

Present day experiments aimed at measuring $\dot G/G$ are not yet
sensitive enough to confirm or refute Dirac's suggestion. However,
there are two good reasons to doubt that $G$ is changing at this rate.
First, if $G$ scales like a power of $t$, then $G$ was vastly larger in
the early universe. This would ruin the successful calculations of
nucleosynthesis in the big bang. Second, the measurements of $\dot \alpha/\alpha$
($\alpha$ is the ordinary fine structure constant, $\alpha = e^2/\hbar c$), are far more
accurate than the measurements of $\dot G/G$. (A recent review has been
given by Dyson.\textsuperscript{20}) A change in $X$ would produce a change in $\alpha$ through
renormalization effects,\textsuperscript{14} at a rate which is ruled out by experiment
if $X$ is changing as rapidly as Dirac's approach to the hierarchy problem
would require.

It is therefore most prudent to assume that the potential energy
$V(X)$ has a stable minimum at some large but finite $X$.

All of this, however, requires a note of caution. In particle
physics discussions we usually ignore gravity. We argue that the
Planck mass is larger than other masses of interest; but the real
reason for ignoring gravity is, of course, that we simply do not know
how to take gravitational effects into account. In the approach I
have been discussing, it is not at all clear that it is valid to neglect
gravity. As I have explained, in this approach the ``bare''
Planck mass should probably be of order $M$, the fundamental mass scale
of the theory. The observed Planck mass is then larger in today's
universe because of a sort of renormalization effect --- the large,

% VERIFY: Original p. 351 ends mid-sentence after ``the large,'' and the continuation is on p. 352.
